Title

### 2019-05-08 4_method.tex
lil update on angle of introduced ribs

\subsection{5. Add bones for introduced joints}
\textcolor{gray}{
\paragraph{Angle of fingers introduced on the skeleton}
\Cref{finger_angles}
Cannot be optimized.
Always has to be orthogonal to the polygon segment.
Otherwise the algorithm isn't stable w.r.t. extra vertices in the outline.
}
\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\caption{Stability against extra vertices}
\label{finger_angles_stability}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal to the outlines}
\label{finger_angles}
\end{figure}

>>>>

\subsection{5. Add bones for introduced joints}
\textcolor{gray}{
\paragraph{Angle of fingers introduced on the skeleton}
\Cref{finger_angles}
Cannot be optimized.
Always has to be orthogonal to the polygon segment.
Otherwise the algorithm isn't stable w.r.t. extra vertices in the outline.
}
\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\caption{Stability against extra vertices}
\label{finger_angles_stability}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\caption{Wrong rib angle, not orthogonal to outline}
\end{subfigure}
\caption{Finger angles should always be orthogonal to the outlines}
\label{finger_angles}
\end{figure}

\begin{wrapfigure}[5]{r}{0.2\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{sources/method/min_angle_of_introduced_bones.pdf}
\end{center}
\end{wrapfigure}

Because the ribs are always orthogonal to the outline segments, the angle $\alpha$ between the spine and ribs is within the range $\SI{60}{\degree} < \alpha < \SI{90}{\degree}$.
